Predicting the manner in which exercises are done
========================================================

Load the data

```{r}
tr <- read.csv("pml-training.csv")
```

Fix numerics imported as character values, dropping the first 7 columns
, which don't represent sensor measurements, but things like time-stamps, user names
, and various other metadata about each data sample.

```{r, message = FALSE, warnings = FALSE}
tr.fix <- tr[,8:160]
tr.fix[,1:152] <- sapply(tr.fix[,1:152], paste)
suppressWarnings(tr.fix[,1:152] <- sapply(tr.fix[,1:152], as.numeric))
```

Drop columns with NAs.

```{r}
na.sums <- apply(tr.fix, 2, function(x) sum(is.na(x)))
rows <- nrow(tr.fix)
tr.fix.nona <- tr.fix[,na.sums == 0]
```

Fit a random forests model to the data.

```{r, message = FALSE, warnings = FALSE}
suppressWarnings(require(randomForest))
set.seed(1975)
fit <- randomForest(classe ~ ., data=tr.fix.nona, na.action=na.roughfix)
```

Let's take a look at the model.

```{r}
fit
```

The OOB estimate represents the expected out of sample error: **0.25%**  

Now let's move to the test data and predict the manner the exercises were done.  

Read and fix the data, leave NAs.

```{r, message = FALSE, warnings = FALSE}
tst <- read.csv("pml-testing.csv")

tst.fix <- tst[,8:159]
tst.fix[,1:152] <- sapply(tst.fix[,1:152], paste)
suppressWarnings(tst.fix[,1:152] <- sapply(tst.fix[,1:152], as.numeric))
```

And finally - predict the test sample classes:

```{r}
answers <- predict(fit, newdata=tst.fix); answers
```
